### 2018-06-07 Project log/multiple_outcomes_project_log.Rmd
Fix functions.R bug in cell_corr that was making results wrong for prop.corr != 1

<!-- NEW SECTION -->
\section{Proof sketch following Freedman paper}

\begin{enumerate}
\item{ Define multivariate Mallows metric, $\tilde{d}_2$. Prove that it's still a metric and that Eq. (2.3) still holds. Since it's a metric, triangle inequality (2.6) still holds:
$$\frac{1}{2} \tilde{d}_2(F_n, F)^2 \le \tilde{d}_2(\widehat{F}_n, F_n) + \tilde{d}_2( F_n, F)$$}

\item{ $\bigstar$ Show that Theorem 2.1 still holds for $\tilde{d}_2$, assuming the same design matrix for all regressions:
$$\tilde{d}_2^p( \Psi (F_n), \Psi (F)) \le n \cdot \text{trace} [X(n)'X(n)]^{-1} \cdot d_2(F,G)$$
}

\item{Work on each piece of the triangle inequality:
	\begin{enumerate}
    	\item $\tilde{d}_2(F_n, F) \to 0$ because we can still apply SLLN to joint distribution (analog to B\&F Lemmas 8.3/8.4).
        \item $\tilde{d}_2( \widehat{F}_n, F_n) \le \frac{p}{n} \sum_{w=1}^W \sigma^2_w \to 0$ (analog to Lemmas 2.1/2.2).
    \end{enumerate}
}

\item{Lemma 2.4 still holds because each term $\to 0$ by B\&F Lemma 2.4:
$$\frac{1}{n} \sum_{w=1}^W \| \widehat{\epsilon}_{w} (n) - \widehat{\epsilon}_{w} (n) \|^2 \to 0$$
}

\item{ Lemma 2.5 still holds using our Eq. (2.3), our Lemma 2.4, and the fact that $\widehat{F}_n = \tilde{F}_n$ for us:

$$d_2( \widehat{F}_n, F_n ) \to 0$$}

\item{$\bigstar$ Show that $\Psi (F_n)$ is close to $\Psi (\widehat{F}_n)$ by writing difference between vector of coefficient estimates in terms of residuals and resampled residuals (loose analog to Theorem 2.2).}
\end{enumerate}

@@

FCR-center works for OLS but not logistic regression because for the latter, SE depends on value of parameter. (Is this subset pivotality?)

Marginally vs. conditionally: See simulation writeups.

Bootstrapping brainteaser: Observations really are independent in FCR resamples. I think the previous issues with this were actually not due to failed assumptions. 
\url{https://stats.stackexchange.com/questions/339237/are-observations-independent-in-bootstrapped-resamples}

@@

@@

>>>>

<!-- NEW SECTION -->

@@

Chatterjee generalized bootstrap paper: This seems to say that for logistic regression \emph{confidence interval} (not under $H_0$), we can sample with replacement from observations' contributions to the score equations, and then solve these new score equations. I don't think it's valid to simply center these test stats as for OLS because, as shown in the FCR-center simulations, the SEs will be wrong. But maybe we could plug in the null values of the parameters into the score equations?

R algorithm:
\begin{enumerate}
\item Write function that calculates score contribution as function of parameters.
\item Setting the parameter of interest to null value, calculate score contribution for each observation. 
\item Find the parameter that solves the new score equations?
\end{enumerate}

Actually, I think we have a broader problem: How do we do bootstrap hypothesis tests with GLMs at all?

Does the Chatterjee paper mean that you can always use FCR to get CIs for any GLM?

@@

\subsection{Why doesn't MICE idea work?}

@@

\subsection{2018-6-6 *more scenarios}

Trying more scenarios to have smaller proportion of effects but still with observed rejections way outside CI.

\begin{itemize}
\item $\rho_{XY} = 0.25$ with 20\% correlated: Has 100\% power, so need to go down. 
\item $\rho_{XY} = 0.25$ with 5\% correlated: Same as above
\item $\rho_{XY} = 0.15$ with 5\% correlated: Same as above
\end{itemize}

\subsection{2018-5-18 *all scenarios Freedman resampling}

These are in the paper.
